\documentclass{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{tgcursor}

\begin{document}
\fontfamily{qcr}\selectfont
\title{Interview Questions}
\author{Karl Solomon}

\maketitle
\small
\begin{itemize}
	\item Hiring Manager:
	      \begin{itemize}
		      \item What values/skills(soft or hard)/core-competencies do you seek in a member of your team?
		      \item How many direct reports do you have? Is this typical at this company?
		      \item Do you expect your team to grow? If yes, do you have an estimate on how large?
		      \item How many direct reports do you think you could manage before feeling overextended?
		      \item How often do you meet with each direct report? For how long?
		      \item What is your background? How did you get to the role that you're in? (linkedin)
			  \item Do you feel like your background sufficiently prepared you to manage this team?
		      \item What skills, tasks, attributes do you think your team could improve upon?
		      \item What skills, tasks, attributes do you want to personally improve upon?
		      \item What is the average tenure on your team?
		      \item Typically how much experience does one have to be at each of the following roles: entry, senior, staff?
		      \item Does the organization require you to do anything like pip certain \% of employees per year, give below-average performance reviews, etc.?
			  \item Are dev environments standardized/forced? E.g. Everyone has to use Win11, Ubuntu, etc.? Or can I choose my own environment?
			  \item What \% of time are your reports doing each of the following tasks: Meetings, Code Review, Documentation, Testing, Refactoring, etc.
			  \item In-person, hybrid, or remote?
		      \item What, if any, team-building activities have you done?
	      \end{itemize}
	\item Dev
	      \begin{itemize}
		      \item Do you have any input on expected timelines for deliverables? How often would you say the expected timeline is reasonable to achieve?
		      \item Take me through the lifecycle of a bugfix/feature request. Include details on how the code review looks.
		            \begin{itemize}
			            \item How many required/optional reviewers per PR?
			            \item CI/CD Pipeline?
			            \item Unit tests?
			            \item Code Coverage?
			            \item Code Formatting?
			            \item Typical time betwen PR open and merge?
			            \item
		            \end{itemize}
		      \item What is the largest bug that's been discovered while you've been at the company? What was the fallout: How did responsible party's (X) manager react? Is X still at the company? Was anyone recalled from vacation?
		      \item Are dev environments standardized/forced? E.g. Everyone has to use Win11, Ubuntu, etc.? Or can I choose my own environment?
		      \item Do you feel the desire to bring a work computer with you on vacation?
		      \item How many hours per week are you in meetings? Do you think the company/team would be better served to have more or less meetings?
		      \item Do you spend time with any coworkers outside of work? Is this a personal choice or standard for the company?
		      \item What tools do you use?
		            \begin{itemize}
			            \item Version Control: Git, SVN, Perforce, BitBucket?
			            \item Build tools: Cmake, Makefiles, IDE-Specific (e.g. ewarm/iar)?
			            \item Compilers: GCC, Clang, MSVC, other?
			            \item Preferred scripting languages: Python, Bash, Batch, other?
			            \item Which architecture do you compile for? x86, arm, riscv?
		            \end{itemize}
		      \item What \% of your time is dedicated to each of the following tasks?
		            \begin{itemize}
			            \item Implementing/debugging new features/drivers
			            \item Writing bugfixes
			            \item Refactoring
			            \item Testing existing functionality
			            \item Documentation
			            \item Code Review
			            \item Meetings
			            \item Other that you feel is non-negligible. What is it?
		            \end{itemize}
	      \end{itemize}
	\item HR
	      \begin{itemize}
		      \item In-person, hybrid, or remote?
		      \item Am I able to view the benefits package before accepting any pending offer?
		      \item Expected start date range?
		      \item Am I able to talk to HR about troubles/concerns I have without things becoming public/political?
		      \item Does the company have plans to grow? If yes, are there any known milestones which you\'re able to share?
	      \end{itemize}
	\item Cross-Functional
	      \begin{itemize}
		      \item How much time do you spend in meetings?
		      \item If you have a feature request or find a bug in the code, how do you relay that to the dev team? How long do things typically take to get fixed or implemented?
		      \item If you had to summarize your relationship to the development team in one word, what would that be?
	      \end{itemize}
	\item Startup-Specific
	      \begin{itemize}
		      \item How does the pay structure look? Has your company ever had to delay payment? If so, for how long and was full payment received as stated in your original contract?
		      \item How many employees do you have? Roughly how many in each of the following areas: HW, SW, Mech, Test, Mgr, HR, Marketing, other?
		      \item What are your short-term and long-term major milestone goals? How likely are you to hit them as things stand currently?
		      \item Is the vision of the founders/execs to be acquired or to sustain a company in the long-term?
		      \item Full-time, part-time, or contract?
		      \item What differentiates your product from competitors (Etched --> Groq (LPU - Language Processing Unit))
	      \end{itemize}
	\item Big Company-Specific
	      \begin{itemize}
		      \item Is it standard to use webcams during meetings? If it depends on size, below what number of attendees would it be expected?
		      \item Is it common to see people changing teams if, for some reason, their current team is not a good fit?
		      \item What level does one need to be at in order to have input to project scope, timelines, etc.?
		      \item Is your team distributed or largely in one location?
		      \item What is one thing you think this company excels at? One thing this company could improve upon?
		      \item How many people per year, do you think, leave your team?
		      \item How does this team compare other teams/companies you've worked for in the past? Both professionally and personally?
		      \item Are bugs usually assigned to the original developer or whoever has bandwidth?
		      \item Who at the company do you wish you had more access to? How could that be improved?
		      \item How do you show what value-add you have to the team/company? Is it based on number of bugs closed, lines contributed/deleted, major milestones achieved, etc.?
		      \item Do you feel like your EOY review is based entirely on things within your control, or does it depend on team/product/company performance?
	      \end{itemize}
\end{itemize}
\end{document}
\enddocument
